---
title: "Exploring Statistics"
author: "Aitor Alexander Gutierrez Valero"
date: "2022-08-16"
output: 
  prettydoc::html_pretty:
    theme: architect
    highlight: github
---

```{r setup, include=FALSE}
library(knitr)
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
```

## Foundational Concepts

---

### Population, Sample, and Sample Size

<span style="color: black;">
A population is a defined set of individuals, and a sample is a randomly selected sub-set of a population. For example: As of 2022, Spain has [4.7M](https://www.ine.es/dyngs/INEbase/es/operacion.htm?c=Estadistica_C&cid=1254736176951&menu=ultiDatos&idp=1254735572981) people. A sample of the Spanish population would be a random selection of 1 - to - 4.69M people in Spain.
</span>

<span style="color: black;">
Sample size determines the accuracy of any data calculated from a sample. This accuracy can be split into two concepts:</span>

<span style="color: black;">
Confidence Level
</span>

    Certainty that our sample represents the population

<span style="color: black;">
Error Margin
</span>

    Certainty that our statistics reflect the population's views


```{r}
```
