---
title: "Exploring Statistics"
author: "Aitor Alexander Gutierrez Valero"
date: "2022-08-16"
output: 
  prettydoc::html_pretty:
    theme: architect
    highlight: github
---

```{r setup, include=FALSE}
library(knitr)
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
```

# Foundational Concepts

---

## Population, Sample, and Sample Size


A population is a defined set of individuals, and a sample is a randomly selected sub-set of a population. For example: As of 2022, Spain has [4.7M](https://www.ine.es/dyngs/INEbase/es/operacion.htm?c=Estadistica_C&cid=1254736176951&menu=ultiDatos&idp=1254735572981) people. A sample of the Spanish population would be a random selection of 1 - to - 4.69M people in Spain.

Sample size determines the accuracy of any data calculated from a sample. This accuracy can be split into two concepts:


**Confidence Level -**

    Certainty that our sample represents the population


**Error Margin -**

    Certainty that our statistics reflect the population's views


To further elaborate: We find that the average weight of all Spaniards is 70 kg with an error margin of 10% and a confidence level of 95%. The error margin means that the weight is actually somewhere between 63 and 77 kg, and the confidence level means that we are 95% sure that the average is between 63 and 77 kg.


Below is a table comparing the error margin and confidence level for different sample sizes of a population of 1 million people.
```{r, echo=FALSE}
#Confidence levels of 90, 95, and 99
#Error margins of 15, 10, and 5
#Sample Sizes of
sample_size <- c(31, 97, 664, 16317)
error_margin <- c(15, 10, 5, 1)
confidence_level <- c(90, 95, 99, 99)

sample_df <- data.frame(sample_size, error_margin, confidence_level)
colnames(sample_df) <- c("Sample Size", "Error Margin", "Confidence Level")

kable(sample_df)
```

---

## Statistics vs. Parameters
**Statistics -**

    The calculated values from a sample

**Parameters -**

    The true values from a population (Calculable if your sample is the population)

---

## Variable Types used in Statistics (Types of data)

#### Qualitative (Categorical)
**Ordinal -**

    An ordered set of variables: Always, frequently, sometimes, etc.

**Nominal -**

    An unordered variable: Gender, Colour, Country, etc.

#### Quantitative
**Continuous -**

    Numerical: Infinite values like height and weight

**Discrete -**

    Numerical: Countable values like number of people or flowers

---

## Three Types of Statistics Analysis

Statistics analysis is used to interpret, represent, and extrapolate data and its various trends.


### 1. Bias

Defines how error influences the final results.

**Random Error -**

     Uncontrollable error in measurement that varies randomly
     For example: Value is between smallest increments; rounded up or down

**Systematic Error -**

    Error in measurement that skews values consistently
    For example: Scale consistently measures too high by 1 kg.

### 2. Descriptive Statistics

Provides an idea of the differences or similarities between data by defining averages and spread.

Below is a data set of numbers for which we will calculate descriptive statistics. First are the averages, next is the spread.

    -7, 1, 2, 2, 3, 4, 5, 5, 6, 22
    
```{r, echo=FALSE}
#Data Set of -7,1,2,2,3,4,5,5,6,22

#Type
#Definition of Mean "Measure of Location"
#Definition of Median
#Definition of Mode

Type <- c("Description", "Example", "Result")
Mean <- c("Sum of all of the numbers divided by the number of numbers", "(-7 + 1 + 2 + ... + 22)/10", 4.3)
Median <- c("Value separating the upper and lower halves", "Mean of 3 and 4", 3.5)
Mode <- c("Most frequent value in a dataset", "Bimodal", "2 and 5")

location_measure <- data.frame(Type, Mean, Median, Mode)

kable(location_measure)
```


