---
title: "Exploring Statistics"
author: "Aitor Alexander Gutierrez Valero"
date: "2022-08-16"
output: 
  prettydoc::html_pretty:
    theme: architect
    highlight: github
---

```{r setup, include=FALSE}
library(knitr)
library(tidyverse)
knitr::opts_chunk$set(echo = TRUE)
```

# Foundational Concepts

---

## Population, Sample, and Sample Size


A population is a defined set of individuals, and a sample is a randomly selected sub-set of a population. For example: As of 2022, Spain has [4.7M](https://www.ine.es/dyngs/INEbase/es/operacion.htm?c=Estadistica_C&cid=1254736176951&menu=ultiDatos&idp=1254735572981) people. A sample of the Spanish population would be a random selection of 1 - to - 4.69M people in Spain.

Sample size determines the accuracy of any data calculated from a sample. This accuracy can be split into two concepts:


Confidence Level

    Certainty that our sample represents the population


Error Margin

    Certainty that our statistics reflect the population's views


To further elaborate: We find that Spaniards weigh 70 kg on average with an error margin of 10% and a confidence level of 95%. The error margin means that the average Spaniard weighs somewhere between 63 and 77 kg, and the confidence level means that we are 95% sure that the average Spaniard weighs between 63 and 77 kg.


Below is a table comparing the error margin and confidence level for different sample sizes of a population of 1 million people.
```{r, echo=FALSE}
#Confidence levels of 90, 95, and 99
#Error margins of 15, 10, and 5
#Sample Sizes of
sample_size <- c(31, 97, 664, 16317)
error_margin <- c(15, 10, 5, 1)
confidence_level <- c(90, 95, 99, 99)

sample_df <- data.frame(sample_size, error_margin, confidence_level)
colnames(sample_df) <- c("Sample Size", "Error Margin", "Confidence Level")

kable(sample_df)
```

---

## Variable Types used in Statistics (Types of data)

#### Qualitative (Categorical)
Ordinal - An ordered set of variables: Always, frequently, sometimes, etc..

Nominal - An unordered variable: Gender, Colour, Country, etc..

#### Quantitative
Continuous - Numerical: Infinite values like height and weight

Discrete - Numerical: Countable values like number of people or flowers

